PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-02-28 qfenv_paper/qf_environment.tex
Began changes in Section 3

With the target galaxy population divided into quiescent and star-forming galaxies 
in dense and sparse environments, we calculate the stellar mass functions 
(SMFs) for each of these subsamples. % should I include any conclusions on SMF in the abstract? 
With these SMFs, we compute the $f_{\rm{Q}}$s to find that at 
$\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ increases by $\sim 0.15$ from 
$z=0.8$ to $0.0$ for both high and low environments. 
In addition, throughout the redshift range the difference between the
$f_{\rm{Q}}$ at high and low environment remains constant at $< 0.1$. 
These results suggest that while $f_{\rm{Q}}$ increases for galaxies in 
both dense and sparse environments over redshift, the evolution of $f_{\rm{Q}}$ 
is independent of environment. 
%The SMF evolution suggests that in dense environments over the redshift range $z=0.8$ to $0.0$, the SMF of 
%quiescent galaxies increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ 
%while the SMF of the star-forming galaxies evolves little for all masses. Meanwhile in low 
%density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
%galaxies evolves little for all stellar masses and the SMF of star-forming 
%galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.  
\end{abstract}

@@

\section{Sample Selection}
In this paper we are interested in measuring the evolution of the quiescent 
fraction over a wide range of redshifts and in different galaxy environments. 
In order construct a sample with redshift depth and robust enough redshift values 
to measure galaxy environment, we use galaxies at intermediate redshifts from PRIMUS. 
Additionally we supplement our sample with galaxies at low redshift ($z \sim 0.1$) from SDSS.

@@

\subsection{Galaxy Environment} \label{sec:environment}
In addition to the quiescent/star-forming classification, we now measure the environment for the target galaxy sample. 
First, we define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
As our aperture, we use a cylinder with dimensions with $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. 
Though spherical apertures are often used in literature (e.g. \cite{Croton:2005aa}), we use a cylindrical aperture in order to 
account for the PRIMUS redshift errors and redshift space distortions.  
Furthermore, we use a cylinder with the specified dimensions based on scale dependence for clustering analysis done in 
\cite{Blanton:2006aa}, which suggests that galactic properties such as star-formation histories are dependent on properties
 such as the masses of their host dark matter halos.
Hence, with cylindrical apertures of $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ we are able to probe the local small scale environment 
within the scales of the host dark matter halos.
We extend our analysis to cylindrical apertures with cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$; however 
we find that the variation in $R_{\rm{ap}}$ does not change our results significantly (difference in $f_{Q} < 0.05$). 
Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}). 
%include a sentence that sums up everything in Croton and Muldrew?

@@

\section{Results}
In this section, we describe our calculation to obtain the stellar mass functions (SMF) and quiescent fraction (QF) using the stellar mass complete target population.
In Section \ref{sec:smf_const} we construct the non-parametric estimate of SMFs for star-forming and quiescent galaxies in redshift bins: $0.06-0.145$, $0.2-0.4$, 
$0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
Form these SMFs, we calculate the QFs in section \ref{sec:qf_const}.

\subsection{Stellar Mass Function} \label{sec:smf_const}
Our primary interest in the SMFs is to investigate the evolution of the quiescent fraction in different density environments over our redshift range. 
Hence, we first divide the target galaxy sample into quiescent and star-forming target samples using the classification scheme from Section \ref{sec:sfq}.
Both the quiescent and star-forming target samples are then divided into "high-environment","mid-environment", and "low-environment" based on their environment classification described in 
Section \ref{sec:environment}.
We use the five redshift bins described in \ref{target} to get a total of $30$ subsamples that are classified based on star-forming/quiescent, environment, and redshift.
For each of these subsamples, we calculate the SMFs and their errors.

@@

>>>>

With the target galaxy population divided into quiescent and star-forming galaxies 
in dense and sparse environments, we calculate the stellar mass functions 
(SMFs) for each of these subsamples. % should I include any conclusions on SMF in the abstract? 
With these SMFs, we compute the $f_{\rm{Q}}$s to find that at 
$\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ increases by $\sim 0.15$ from 
$z=0.8$ to $0.0$ for both high and low environments. 
In addition, throughout the redshift range the difference between the
$f_{\rm{Q}}$ at high and low environment remains constant at $< 0.1$. 
These results suggest that while $f_{\rm{Q}}$ increases for galaxies in 
both dense and sparse environments over redshift, the evolution of $f_{\rm{Q}}$ 
is independent of environment. 
\end{abstract}

@@

\section{Sample Selection} \label{sec:sample}
In this paper we are interested in measuring the evolution of the quiescent 
fraction over a wide range of redshifts and in different galaxy environments. 
In order construct a sample with redshift depth and robust enough redshift values 
to measure galaxy environment, we use galaxies at intermediate redshifts from PRIMUS. 
Additionally we supplement our sample with galaxies at low redshift ($z \sim 0.1$) from SDSS.

@@

\subsection{Galaxy Environment} \label{sec:environment}
In addition to the quiescent/star-forming classification, we now measure the environment for the target galaxy sample. 
First, we define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
As our aperture, we use a cylinder with dimensions with $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. 
Though spherical apertures are often used in literature (e.g. \cite{Croton:2005aa}), we use a cylindrical aperture in order to 
account for the PRIMUS redshift errors and redshift space distortions.  
Furthermore, we use a cylinder with the specified dimensions based on scale dependence for clustering analysis done in 
\cite{Blanton:2006aa}, which suggests that galactic properties such as star-formation histories are dependent on properties
 such as the masses of their host dark matter halos.
Hence, with cylindrical apertures of $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ we are able to probe the local small scale environment 
within the scales of the host dark matter halos.
We extend our analysis to cylindrical apertures with cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$; however 
we find that the variation in $R_{\rm{ap}}$ does not change our results significantly (difference in $f_{Q} < 0.05$). 
Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}). 
%include a sentence that sums up everything in Croton and Muldrew? 
%Also include remarks on Wilman et al.

@@

\section{Results}
In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
and examine it's evolution over our redshift range.

\subsection{Stellar Mass Function} \label{sec:smf_const}
The target galaxy sample defined above has so far
been classified into quiescent or star-forming and 
dense or sparse. We further divide these subsamples 
into bins of redshift:  in redshift bins of $0.06-0.145$, 
$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
PRIMUS data ranges from $0.2 < z < 1.2$, we only 
consider galaxies with $ z<0.8$ due to insufficient
statistics for robust environment measurements at 
higher redshifts. With added redshift bins, we have a
total of 16 subsamples. We calculate the SMF for 
each of these 16 subsamples.

@@

%The SMF evolution suggests that in dense environments over the redshift range $z=0.8$ to $0.0$, the SMF of 
%quiescent galaxies increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ 
%while the SMF of the star-forming galaxies evolves little for all masses. Meanwhile in low 
%density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
%galaxies evolves little for all stellar masses and the SMF of star-forming 
%galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.
